---
title: "My First R Presentation"
author: "Abhijit Jantre"
date: "December 2, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slide
New Content
Plain Text

*Italicized text*

**Bold text**

`for (i %in% 1:10)`

## My Title

### A Top Level Sub-heading
- Bullet 1

#### A Second Level Sub-heading
- Bullet 2

*** 
Slide without heading
# Here eval =TRUE by default
```{r}             
head(iris,3)
```

```{r, comment="", eval=FALSE}
head(iris,2)

```

```{r, comment=""}
head(mtcars,2)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r, echo=TRUE,fig.align='center',fig.cap='My Analysis'}
plot(mtcars$wt,mtcars$mpg,xlab = "Weight", ylab = "MPG")
```

